Geometric variational problems

### 2020-11-15 NSF2020/Description/newspecificaim2.tex
RJR educational impact
4.2.1 edited

\subsection{Specific Aim 2: Efficient high-order numerical methods for
large-scale simulations}
\label{subsec:specific_aim_2}
%\begin{figure}[h]
\begin{wrapfigure}[13]{r}{0.61\textwidth}
  \centering{\includegraphics[width=0.61\textwidth]{Figures/domain.pdf}}
    \vspace{-20pt}
    \caption{\label{fig:flow_map} \footnotesize The diagram depicts a collection of 3D
    amphiphilic particles suspended in a solvent. The solvent velocity satisfies
    the Stokes equations, and the hydrophobic forces depend on the
    solvent activity that satisfies the screened Laplace equation. The
    geometry is updated by solving the mobility problem.} 
\end{wrapfigure}
%\end{figure}
% ----------------------------------------------------------------------
Over the past decade, there has been an explosion of interest in
small-scale processes that utilize capillary forces and van der Waals
interactions to coordinate movement
and bind microscopic components in solvent~\cite{Pandey2011, Zhang2017, Siontorou2017}.
Additionally, hydrodynamic interactions are central to fabricating complex,
three-dimensional microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010}.
Hydrodynamic effects cannot
be ignored since they, like for the rates of biological functions 
like pore dynamics~\cite{RYHAM20112929}, set the rate of dissipation.
%
In Specific Aim 2, we propose to develop efficient high-order numerical
methods to simulate dynamic assembly of particles under HAP potential in
a viscous solvent. 
%
%
%hydrodynamics effects by em
%particles in a solvent. 
%
% Results from these proposed numerical simulations will be useful to 
% Finally, coarse-grained and molecular
%dynamics theories include water either explicitly or implicitly in their
%models. 
%
%The immediate goal of the present proposal is to simulate
%vesicle bilayers in external flows, where the bilayers are represented
%by a self-assembled collection of rigid particles.
%
As described in~\eqref{eq:stokes} and illustrated in
Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
equations for an incompressible, viscous fluid, and these equations are
coupled to the screened-Laplace equation~\eqref{SL} through viscous and
hydrophobic stress balance.

@@

The HAP model requires solving exterior Dirichlet problems for the
screened Laplace equation and the Stokes mobility problem at each time
step in complex domains such as in Figure~\ref{fig:domain}. If
discretizing these equations with stencil-based numerical methods, the
computational domain must be truncated, the fluid volume must be
discretized, and artificial boundary conditions must be imposed. The
artificial boundary conditions introduce additional error, and
discretizing the volume results in an excessively large system of
equations. Moreover, it is difficult to obtain high-order
discretizations when the boundary surfaces are irregular. Alternatively,
since we are solving constant-coefficient linear elliptic
partial differential equations (PDEs), their
solutions can be represented with layer potentials
\begin{align}
  \label{eq:LP}
  u(\mathbf{x}) = \int_{\partial\Omega} K(\mathbf{x},\mathbf{y})
  \sigma(\mathbf{y})\,dS,
\end{align}
where $\sigma$ is an unknown density function, and
$K(\mathbf{x},\mathbf{y})$ is a derivative of the fundamental solution
of the PDE. By matching the prescribed boundary condition at
$\mathbf{x}_0 \in \partial\Omega$ with the limit of
equation~\eqref{eq:LP} as $\mathbf{x}\rightarrow \mathbf{x}_0$, a
boundary integral equation (BIE) for the density function is formed.

@@

Discretizations of carefully chosen BIEs can be solved with a
mesh-independent number of GMRES
iterations~\cite{cam-ips-kel-mey-xue1996}. Therefore, the required CPU
time is proportional to the cost of a matrix-vector multiplication that
can be performed in optimal or near-optimal time with the fast multipole
method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2, fmm3,
fmm4, fmm6, fmm7, fmm8}. PI BQ is experienced with applying FMMs for the
Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the screened
Laplace equation~\cite{kro-qua2011, qua2011}.  Alternatively, fast
direct solvers avoid iteration~\cite{fds2, fds3, fds4, fds5, fds6, fds7,
ho2016cpam1, minden2016, minden2017siammms}, but direct solvers often
require a large amount of computational overhead, and this makes them
less practical for problems with moving geometries. Alternatively, fast
direct solvers techniques can be used to develop efficient
preconditioning strategies such as the inverse Fast Multipole Method
(IFMM)~\cite{cou-pou-dar2017}. PI BQ used the IFMM to precondition
Stokes equations~\cite{qua-cou-dar2018}. A suite of other
preconditioners including sparse approximate inverses~\cite{che2000} and
multigrid~\cite{hem-sch1981, sch1982} will be investigated.

%
\begin{wrapfigure}[21]{r}{2.5in}
%\vspace*{+15pt}
\centerline{\includegraphics[width=2.5in]{figures/integrands}}
\vspace*{-13pt}
  \caption{{\footnotesize The Fourier modes of
  $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ where
  $|\mathbf{x_0}| = 0.99$, $\mathbf{y} \in \partial\Omega$, and
  $\Omega$ is the unit disk. The trapezoid rule applied to the red
  integrand has large amounts of error, but the trapezoid rule is much
  more accurate when applied to the blue integrand. Since the difference
  between the red and blue curves can be accurately computed with the
  barycentric quadrature rule, the quadrature error applied to layer
  potentials for the screened Laplace equation will be uniformly bounded
  in $\Omega$.}}
\label{fig:integrands}
\end{wrapfigure}
Nearly touching bodies is ubiquitous in self-assembly of amphiphilic
particles, and this results in nearly-singular integrands. Quadrature
methods for these integrands have received a lot of attention in two and
three dimensions~\cite{alpert, kapur, sidi, duffy, bruno1, bruno2,
davis_1984, graglia_2008, hackbusch_sauter_1994, jarvenpaa_2003,
khayat_2005, schwab_1992, ying_2006, beale1, schwab_1992, ggq1, ggq2,
ggq3, helsing_2008a, helsing_tutorial_2012, klockner2013jcp, qbx2,
wala2019jcp, af2018sisc, siegel2018jcp, rachh2017jcp, ding2019arxiv,
bar2014}. The trapezoid rule is the workhorse for two-dimensional BIEs
since it achieves spectral accuracy when integrands are not
nearly-singular~\cite{tre-wei2014}. To address nearly-singular
integrands of two-dimensional BIEs, we will use a {\em barycentric
quadrature rule} that only requires a slight modification of the
trapezoid rule~\cite{ioa-pap-per1991}. In its current form, this method
requires the layer potential to satisfy Laplace or Stokes
equations~\cite{bar-wu-vee2015, chi-moo-qua2020}, but the PIs will
extend the method to layer potentials for the screened Laplace equation.
This will be done by recognizing that the fundamental solution of the
screened Laplace equation can be decomposed as $K(\mathbf{x},\mathbf{y})
= K_1(\mathbf{x},\mathbf{y}) + K_2(\mathbf{x},\mathbf{y})$, where
$K_1(\mathbf{x},\mathbf{y}) = -\log|\mathbf{x} - \mathbf{y}|$ and
$K_2(\mathbf{x},\mathbf{y}) = K(\mathbf{x},\mathbf{y}) + \log|\mathbf{x}
- \mathbf{y}|$. Then, layer potentials involving
$K_1(\mathbf{x},\mathbf{y})$ can be accurately computed with the
barycentric quadrature rule~\cite{ioa-pap-per1991}, and layer potentials
involving $K_2(\mathbf{x},\mathbf{y})$ can be accurately computed with
the trapezoid rule since the kernel is bounded for all $\mathbf{x}$ and
$\mathbf{y}$. The proposed method is demonstrated in
Figure~\ref{fig:integrands}, where the amplitude of the Fourier modes of
$K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ are
plotted. The quadrature error of the trapezoid rule is the sum of the
unresolved Fourier modes.

>>>>

\subsection{Specific Aim 2: Efficient high-order numerical methods for
large-scale simulations}
% ----------------------------------------------------------------------
Over the past decade, there has been an explosion of interest in
small-scale processes that utilize capillary forces and van der Waals
interactions to coordinate movement
and bind microscopic components in solvent~\cite{Pandey2011, Zhang2017, Siontorou2017}.
Additionally, hydrodynamic interactions are central to fabricating complex,
three-dimensional microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010}.
Hydrodynamic effects cannot
be ignored since they, like for the rates of biological functions 
like pore dynamics~\cite{RYHAM20112929}, set the rate of dissipation.
%
In Specific Aim 2, we propose to develop efficient high-order numerical
methods to simulate dynamic assembly of particles under HAP potential in
a viscous solvent. 
%
%
%hydrodynamics effects by em
%particles in a solvent. 
%
% Results from these proposed numerical simulations will be useful to 
% Finally, coarse-grained and molecular
%dynamics theories include water either explicitly or implicitly in their
%models. 
%
%The immediate goal of the present proposal is to simulate
%vesicle bilayers in external flows, where the bilayers are represented
%by a self-assembled collection of rigid particles.
%
As described in~\eqref{eq:stokes} and illustrated in
Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
equations for an incompressible, viscous fluid, and these equations are
coupled to the screened-Laplace equation~\eqref{SL} through viscous and
hydrophobic stress balance.

@@

\label{subsec:specific_aim_2}
%\begin{figure}[h]
\begin{wrapfigure}[14]{r}{0.61\textwidth}
  \centering{\includegraphics[width=0.61\textwidth]{Figures/domain.pdf}}
    \vspace{-20pt}
    \caption{\label{fig:flow_map} \footnotesize The diagram depicts a collection of 3D
    amphiphilic particles suspended in a solvent. The solvent velocity satisfies
    the Stokes equations, and the hydrophobic forces depend on the
    solvent activity that satisfies the screened Laplace equation. The
    geometry is updated by solving the mobility problem.} 
\end{wrapfigure}
%\end{figure}
The HAP model requires solving exterior Dirichlet problems for the
screened Laplace equation and the Stokes mobility problem at each time
step in complex domains such as in Figure~\ref{fig:domain}. If
discretizing these equations with stencil-based numerical methods, the
computational domain must be truncated, the fluid volume must be
discretized, and artificial boundary conditions must be imposed. The
artificial boundary conditions introduce additional error, and
discretizing the volume results in an excessively large system of
equations. Moreover, it is difficult to obtain high-order
discretizations when the boundary surfaces are irregular. Alternatively,
since we are solving constant-coefficient linear elliptic
partial differential equations (PDEs), their
solutions can be represented with layer potentials
\begin{align}
  \label{eq:LP}
  u(\mathbf{x}) = \int_{\partial\Omega} K(\mathbf{x},\mathbf{y})
  \sigma(\mathbf{y})\,dS,
\end{align}
where $\sigma$ is an unknown density function, and
$K(\mathbf{x},\mathbf{y})$ is a derivative of the fundamental solution
of the PDE. By matching the prescribed boundary condition at
$\mathbf{x}_0 \in \partial\Omega$ with the limit of
equation~\eqref{eq:LP} as $\mathbf{x}\rightarrow \mathbf{x}_0$, a
boundary integral equation (BIE) for the density function is formed.

@@

%
\begin{wrapfigure}[21]{r}{2.5in}
%\vspace*{+15pt}
\centerline{\includegraphics[width=2.5in]{figures/integrands}}
\vspace*{-13pt}
  \caption{{\footnotesize The Fourier modes of
  $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ where
  $|\mathbf{x_0}| = 0.99$, $\mathbf{y} \in \partial\Omega$, and
  $\Omega$ is the unit disk. The trapezoid rule applied to the red
  integrand has large amounts of error, but the trapezoid rule is much
  more accurate when applied to the blue integrand. Since the difference
  between the red and blue curves can be accurately computed with the
  barycentric quadrature rule, the quadrature error applied to layer
  potentials for the screened Laplace equation will be uniformly bounded
  in $\Omega$.}}
\label{fig:integrands}
\end{wrapfigure}
Discretizations of carefully chosen BIEs can be solved with a
mesh-independent number of GMRES
iterations~\cite{cam-ips-kel-mey-xue1996}. Therefore, the required CPU
time is proportional to the cost of a matrix-vector multiplication that
can be performed in optimal or near-optimal time with the fast multipole
method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2, fmm3,
fmm4, fmm6, fmm7, fmm8}. PI BQ is experienced with applying FMMs for the
Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the screened
Laplace equation~\cite{kro-qua2011, qua2011}.  Alternatively, fast
direct solvers avoid iteration~\cite{fds2, fds3, fds4, fds5, fds6, fds7,
ho2016cpam1, minden2016, minden2017siammms}, but direct solvers often
require a large amount of computational overhead, and this makes them
less practical for problems with moving geometries. Alternatively, fast
direct solvers techniques can be used to develop efficient
preconditioning strategies such as the inverse Fast Multipole Method
(IFMM)~\cite{cou-pou-dar2017}. PI BQ used the IFMM to precondition
Stokes equations~\cite{qua-cou-dar2018}. A suite of other
preconditioners including sparse approximate inverses~\cite{che2000} and
multigrid~\cite{hem-sch1981, sch1982} will be investigated.

Nearly touching bodies is ubiquitous in self-assembly of amphiphilic
particles, and this results in nearly-singular integrands. Quadrature
methods for these integrands have received a lot of attention in two and
three dimensions~\cite{alpert, kapur, sidi, duffy, bruno1, bruno2,
davis_1984, graglia_2008, hackbusch_sauter_1994, jarvenpaa_2003,
khayat_2005, schwab_1992, ying_2006, beale1, schwab_1992, ggq1, ggq2,
ggq3, helsing_2008a, helsing_tutorial_2012, klockner2013jcp, qbx2,
wala2019jcp, af2018sisc, siegel2018jcp, rachh2017jcp, ding2019arxiv,
bar2014}. The trapezoid rule is the workhorse for two-dimensional BIEs
since it achieves spectral accuracy when integrands are not
nearly-singular~\cite{tre-wei2014}. To address nearly-singular
integrands of two-dimensional BIEs, we will use a {\em barycentric
quadrature rule} that only requires a slight modification of the
trapezoid rule~\cite{ioa-pap-per1991}. In its current form, this method
requires the layer potential to satisfy Laplace or Stokes
equations~\cite{bar-wu-vee2015, chi-moo-qua2020}, but the PIs will
extend the method to layer potentials for the screened Laplace equation.
This will be done by recognizing that the fundamental solution of the
screened Laplace equation can be decomposed as $K(\mathbf{x},\mathbf{y})
= K_1(\mathbf{x},\mathbf{y}) + K_2(\mathbf{x},\mathbf{y})$, where
$K_1(\mathbf{x},\mathbf{y}) = -\log|\mathbf{x} - \mathbf{y}|$ and
$K_2(\mathbf{x},\mathbf{y}) = K(\mathbf{x},\mathbf{y}) + \log|\mathbf{x}
- \mathbf{y}|$. Then, layer potentials involving
$K_1(\mathbf{x},\mathbf{y})$ can be accurately computed with the
barycentric quadrature rule~\cite{ioa-pap-per1991}, and layer potentials
involving $K_2(\mathbf{x},\mathbf{y})$ can be accurately computed with
the trapezoid rule since the kernel is bounded for all $\mathbf{x}$ and
$\mathbf{y}$. The proposed method is demonstrated in
Figure~\ref{fig:integrands}, where the amplitude of the Fourier modes of
$K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ are
plotted. The quadrature error of the trapezoid rule is the sum of the
unresolved Fourier modes.

### 2020-11-15 NSF2020/Description/specificaim1_ver2.tex
removed last instance of HARP
4.2.1 edited

%\begin{center}
%Anticipated model simulations
%\end{center}
\subsubsection{Simulations of the HARP model to estimate elastic moduli and energy}
%To characterize material properties of a bilayer, we compare the energies and forces generated by
%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
We propose to
%
%to examine conduct calculations similar to the example of figure~\ref{fig:flattening}
%for a wide range of particle parameters and physical parameters in HARP to 
%
%{\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
%as the corresponding energies in the particle system for all reasonable deformation.
%If this is the case we will 
%
{\bf (i)} determine the value of effective elastic moduli $\KB$,
$\KT$, $\KG$, and $\KTH$ and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and
particle shape map onto elastic moduli. 
An accurate and robust way to measure material properties is to track the evolution of the bilayer as
%
\begin{wrapfigure}[10]{r}{0.4\textwidth}
\vspace{-0.3cm}
\centerline{\includegraphics[width=0.4\textwidth]{Figures/Flattening.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
\vspace{-0.2cm}
\caption{\label{fig:flattening} \footnotesize Example of computing
  bending modulus of a lipid bilayer from particle simulation.}
\end{wrapfigure}
it relaxes from an initially non-equilibrium
configuration~\cite{PhysRevLett.117.188102}. Figure~\ref{fig:flattening}
shows an example where the initial configuration of a lipid bilayer
patch contains only splay deformation without any other components
(saddle splay, twist and tilt). As the bent membrane flattens, we find
that both the membrane self-interaction energy $\Phi$ and the elastic
energy ${\cal W}$ decrease, and because the saddle splay, twist, and
tilt stay zero, the slope gives the bending modulus in this case.

@@

%  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
%  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
%  and accounting for these couplings by Taylor expansion  
%  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.
%
%The form of the elastic energy density \eqref{ansatz3} is the same as
%  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
%  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
%  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
%  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
%  Using this observation, we prove an exact identity 
%  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
%  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
%  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.
%  
%%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
%%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
%%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
%%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
%%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
%%  This gives the continuum elastic energy equals
%%  \begin{equation}
%%    \label{eq:twist_energy}
%%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
%%  \end{equation}
%%  which we compare to the HAP simulation data.
%
\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
The HAP energy converges to the surface energy in the limit of vanishing screening length~\cite{Shibata2004}.
Also, the boundary layers of the solutions to the screen Laplace equation
converge to area measures supported on the particle boundaries \cite{Lee2018, Lin2015, Shibata2004}.
These phenomena are analogous to the sharp interface limit in the phase-field functional,
and motivate developing the mathematical connections between the HAP energy and
the energy functionals used in the gradient theory of phase transitions.
formulation~\cite{Modica87, MODICA1987487, LuMo89}.
PI RR has worked on phase field approximations of membrane bending
energy~\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman
equation~\cite{1531-3492_2006_2_357, Lee2018}.
The screened-Laplace equations~\eqref{SL} is the linearization of the Poisson-Boltzmann equation.
One set of questions is to establish the HAP convergence rate as a
function of particle geometry~\cite{LuMo89}, which can be used as a
benchmark for numerical validation.
Ultimately, we will be able to address the so-called $\Gamma$-convergence of energy minimizing
particle configurations in the zero-decay length limit \cite{Roger2006, Mugnai2013}. 
%The phase field functional approximates the perimeter of sublevel sets
%of a so-called phase field indicator function. The approximation becomes
%sharp in the zero interfacial thickness limit and minimizers of the
%phase field functional converge (after normalization) to the
%characteristic function of a set solving a perimeter minimization
%problem
%
%

>>>>

%\begin{center}
%Anticipated model simulations
%\end{center}
\subsubsection{Simulations of the HAP model to estimate elastic moduli
and energy}
%To characterize material properties of a bilayer, we compare the energies and forces generated by
%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
We propose to
%
%to examine conduct calculations similar to the example of figure~\ref{fig:flattening}
%for a wide range of particle parameters and physical parameters in HARP to 
%
%{\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
%as the corresponding energies in the particle system for all reasonable deformation.
%If this is the case we will 
%
{\bf (i)} determine the value of effective elastic moduli $\KB$,
$\KT$, $\KG$, and $\KTH$ and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and
particle shape map onto elastic moduli. 
An accurate and robust way to measure material properties is to track the evolution of the bilayer as
%
\begin{wrapfigure}[10]{r}{0.4\textwidth}
\vspace{-0.3cm}
\centerline{\includegraphics[width=0.4\textwidth]{Figures/Flattening.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
\vspace{-0.2cm}
\caption{\label{fig:flattening} \footnotesize Example of computing
  bending modulus of a lipid bilayer from particle simulation.}
\end{wrapfigure}
it relaxes from an initially non-equilibrium
configuration~\cite{PhysRevLett.117.188102}. Figure~\ref{fig:flattening}
shows an example where the initial configuration of a lipid bilayer
patch contains only splay deformation without any other components
(saddle splay, twist and tilt). As the bent membrane flattens, we find
that both the membrane self-interaction energy $\Phi$ and the elastic
energy ${\cal W}$ decrease, and because the saddle splay, twist, and
tilt stay zero, the slope gives the bending modulus in this case.

@@

%  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
%  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
%  and accounting for these couplings by Taylor expansion  
%  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.
%
%The form of the elastic energy density \eqref{ansatz3} is the same as
%  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
%  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
%  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
%  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
%  Using this observation, we prove an exact identity 
%  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
%  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
%  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.
%  
%%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
%%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
%%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
%%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
%%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
%%  This gives the continuum elastic energy equals
%%  \begin{equation}
%%    \label{eq:twist_energy}
%%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
%%  \end{equation}
%%  which we compare to the HAP simulation data.
%
\subsubsection{Existence of minimizers}
The HK functional \eqref{ansatz3} has had tremendous impact in understanding
biological function, but has received little attention in terms of mathematical
analysis. In the calculus of variations, the principal question is whether a
minimizer of an energy functional exists. But in the case of \eqref{ansatz3},
this answer is presently unknown. With regard to the simpler, Canham-Helfrich
energy, \cite{Simon1993} proved the existence of minimizing surfaces without boundary, 
and \cite{doi:10.1137/18M1195851} proved the well-posedness of a spatially periodic,
time-dependent elastic interface problem. An analytical challenge 
for the HK functional \eqref{ansatz3} is that coupling to a director field makes it
possible to have bounded energy monolayers with corners, and such
pathological examples must be ruled out before carrying over the arguments
for the Canham-Helfrich functional to the present setting.

\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
Our long term goal is to develop tools that can explain functionals like
\eqref{ansatz3} from first principles in terms of HAP. The papers
\cite{doi:10.1063/5.0009734,Seguin2012,Seguin2014} give statistical
mechanical/mean field derivations of the Canham-Helfrich energy from a
pair-potential for rod-like molecules, but do not include tilt, which is an
indispensable deformation at biological scales. To make progress, we must
first understand how the HAP functional behaves under various limits.

We first consider HAP in the limit of vanishing screening length.
As a concrete, model problem we consider a collection of colloidal polyhedral
where the binding energy of this system can be described by a
discrete, lower semicontinuous functional $\Phi_0$ whose value is the total
surface area of the polyhedra minus two times the area of any overlapping faces.
We conjecture that the $\Phi$ energy $\Gamma$-converges to $\Phi_0$
\cite{Mugnai2013}, meaning that any cluster points of minimizers of $\Phi$
converge to a minimum of $\Phi_0$ in the limit $\rho \to 0$. 
To address this conjecture, we employ boundary layer analysis for the screened
Laplace equation \cite{Lee2018, Lin2015, Shibata2004,1531-3492_2006_2_357, Lee2018}.
The technique of $\Gamma$-convergence is a powerful tool for numerical approximations
and with it we can help explain unexcepted phenomena like hierarchical self-assembly \cite{Luo2019}.

%The HAP energy converges to the surface energy in the limit of vanishing screening length~\cite{Shibata2004}.
%Also, the boundary layers of the solutions to the screen Laplace equation
%converge to area measures supported on the particle boundaries \cite{Lee2018, Lin2015, Shibata2004}.
%These phenomena are analogous to the sharp interface limit in the phase-field functional,
%and motivate developing the mathematical connections between the HAP energy and
%the energy functionals used in the gradient theory of phase transitions.
%formulation~\cite{Modica87, MODICA1987487, LuMo89}.
%PI RR has worked on phase field approximations of membrane bending
%energy~\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman
%equation~\cite{1531-3492_2006_2_357, Lee2018}.
%The screened-Laplace equations~\eqref{SL} is the linearization of the Poisson-Boltzmann equation.
%One set of questions is to establish the HAP convergence rate as a
%function of particle geometry~\cite{LuMo89}, which can be used as a
%benchmark for numerical validation.
%Ultimately, we will be able to address the so-called $\Gamma$-convergence of energy minimizing
%particle configurations in the zero-decay length limit \cite{Roger2006, Mugnai2013}. 
%The phase field functional approximates the perimeter of sublevel sets
%of a so-called phase field indicator function. The approximation becomes
%sharp in the zero interfacial thickness limit and minimizers of the
%phase field functional converge (after normalization) to the
%characteristic function of a set solving a perimeter minimization
%problem
%
%
